---
title: "Anthropogenic_Climate"
author: "Zjrobbin"
date: "5/20/2020"
output: html_document
---


```{r}

MPB_Tmax<-read.csv("C:/Users/zacha/Documents/GitHub/IMAP_Python_Project/WPB_Model/WPB_Inputs/MI_Tmax_6_20.csv")
```

```{r setup and functions, include=FALSE}
knitr::opts_chunk$set(echo = F)


library(rgdal)
library(sp)
library(raster)
library(lubridate)



ProcessMeanandVar<-function(Prismpath,Shape,InputFiles){
  Prism<-raster::stack(paste0(Prismpath,InputFiles))
  Shape_t<-spTransform(Shape,crs(Prism))
  #
  #plot(Prism$PRISM_tmean_stable_4kmM3_189501_bil,xlim=c(-125.208,-115),ylim=c(32,40))
  #plot(LL_t,add=T)
  Prism_crop<-crop(Prism,Shape_t)
  Prism_crop<-mask(Prism_crop,Shape_t)
  #plot(Prism_crop$PRISM_tmean_stable_4kmM3_189501_bil)
  #plot(LowMed)
  #plot(LowLow,add=T)
  mean_vector<-cellStats(Prism_crop,stat=mean)
  Tmean_Dataframe<-as.data.frame(cbind(Year,Month,mean_vector))
  Tm_Mean<-aggregate(as.numeric(as.character(Tmean_Dataframe$mean_vector)),
                     by=list(as.numeric(as.character(Tmean_Dataframe$Month))),
                     FUN=mean)
  Tm_Sd<-aggregate(as.numeric(as.character(Tmean_Dataframe$mean_vector)),
                   by=list(as.numeric(as.character(Tmean_Dataframe$Month))),
                   FUN=sd)
  return(list(Tm_Mean$Group.1,Tm_Mean$x,Tm_Sd$x))
}


plotter<-function(Outcome){
  plot(Outcome[[2]],ylim=c(-5,20))
  #qnorm(0.975)*s/sqrt(n)
  points(Outcome[[1]],Outcome[[2]]+(qnorm(0.975)*Outcome[[3]]/sqrt(50)),type="l")
  points(Outcome[[1]],Outcome[[2]]-(qnorm(0.975)*Outcome[[3]]/sqrt(50)),type="l")
}


TmaxCreateNewTemp<-function(Monthvec,delta,Modelname){
  Merge<-cbind(Monthvec,delta)
  colnames(Merge)<-c("Month","Delta")
  Merge2<-cbind(MPB_Tmin$Dates,MPB_Tmin$Month,MPB_Tmax[Modelname])
  colnames(Merge2)<-c("Date","Month",Modelname)
  Merged<-merge(Merge,Merge2,by="Month",all.x=T)
  Merged<-Merged[order(Merged$Date),]
  Outputs<-Merged[2]-Merged[4]
  return(list(Merged$Date,as.numeric(Outputs$Delta)))
}
TminCreateNewTemp<-function(Monthvec,delta,Modelname){
  Merge<-cbind(Monthvec,delta)
  colnames(Merge)<-c("Month","Delta")
  Merge2<-cbind(MPB_Tmin$Dates,MPB_Tmin$Month,MPB_Tmin[Modelname])
  colnames(Merge2)<-c("Date","Month",Modelname)
  Merged<-merge(Merge,Merge2,by="Month",all.x=T)
  Merged<-Merged[order(Merged$Date),]
  Outputs<-Merged[2]-Merged[4]
  return(list(Merged$Date,as.numeric(Outputs$Delta)))
}
```


Historical data from 

http://www.prism.oregonstate.edu/historical/

Time series datasets prior to 1981 are modeled using climatologically-aided interpolation (CAI), which uses the long-term average pattern (i.e., the 30-year normals) as first-guess of the spatial pattern of climatic conditions for a given month or day. CAI is robust to wide variations in station data density, which is necessary when modeling long time series. Data is based on monthly modeling.

These datasets use whatever station networks and data sources are available for the relevant period. 


## Maximum Temperature

```{r Loading in the Temp Max Data }
Drive<-"E:/Historic_climate/"
## set up the years 1895-1945
Years<-seq(1895,1945,1)
## Get the Temperature max files
Tmax_Files<-list.files(paste0(Drive,"PRISM_tmax_stable_4kmM3_189501_198012_bil/"),
           pattern="*.bil$")
## Filter them by the Years
InputFiles<-Tmax_Files[grep(paste(Years,collapse="|"),Tmax_Files)]
## Get the dates, year and month. 
split<-unlist(strsplit(InputFiles,"PRISM_tmax_stable_4kmM3_"))
split<-split[c(F, T)]
Datestring<-unlist(strsplit(split,"_"))
Datestring<-Datestring[c(T,F)]
Year=substr(Datestring,start=1,stop=4)
Month=as.numeric(substr(Datestring,start=5,stop=6))
## Path to the Prism Data
Prismpath<-paste0(Drive,"PRISM_tmax_stable_4kmM3_189501_198012_bil/")
```


```{r, Loading in the shape files }
### Load in the shape files 
HighMed=readOGR(paste0(Drive,
          "Inputs/Shapes/WPB/High_Med.shp"))
HighLow=readOGR(paste0(Drive,
          "Inputs/Shapes/WPB/High_Low.shp"))
LowMed=readOGR(paste0(Drive,
          "Inputs/Shapes/WPB/Low_Med.shp"))
LowLow=readOGR(paste0(Drive,
          "Inputs/Shapes/WPB/Low_Low.shp"))
```

```{r, Proccesing the mean and var Tmax}
#process the prism data for the years 1985-1945 using the shape files
## See function structure above 
LowLow_tmax=ProcessMeanandVar(Prismpath = Prismpath,LowLow,InputFiles = InputFiles)
HighMed_tmax=ProcessMeanandVar(Prismpath = Prismpath,HighMed,InputFiles = InputFiles)
HighLow_tmax=ProcessMeanandVar(Prismpath = Prismpath,HighLow,InputFiles = InputFiles)
LowMed_tmax=ProcessMeanandVar(Prismpath = Prismpath,LowMed,InputFiles = InputFiles)
```

Looking at the historic data(1895-1945): Mean and confidence interval

### Historic

### Then we load in our DayMet data from 2003-2018

```{r}

#head(MPB_Tmax)
MPB_Tmax$Month<-month(MPB_Tmax$Dates)

Future_mean_Tmax<-aggregate(list(LowLow=MPB_Tmax$Low_LowElShape_Out,
                            LowMed=MPB_Tmax$Low_MedElShape_Out,
                            HighLow=MPB_Tmax$High_LowElShape_Out,
                            HighMed=MPB_Tmax$High_MedElShape_Out),
                   by=list(Month=as.numeric(as.character(MPB_Tmax$Month))),
                   FUN=mean)

Future_Sd<-aggregate(list(LowLow=MPB_Tmax$Low_LowElShape_Out,
                      LowMed=MPB_Tmax$Low_MedElShape_Out,
                      HighLow=MPB_Tmax$High_LowElShape_Out,
                      HighMed=MPB_Tmax$High_MedElShape_Out),
                 by=list(Month=as.numeric(as.character(MPB_Tmax$Month))),
                 FUN=mean)
```

Here is the comparison between the monthly mean between the study domain (2003-2018), and the historic nomral (1895-1945).

```{r, plotting historic versus current, fig.width=10.0,fig.height=10.0}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LowLow_tmax[[2]],ylim=c(0,30),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation/Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmax$LowLow,col="red",cex=1.4,pch=19)

plot(LowMed_tmax[[2]],ylim=c(0,30),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation/Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmax$LowMed,col="red",cex=1.4,pch=19)

legend(1,30,legend=c("Monthly Mean 1895-1945","Monthly Mean 2003-2018"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
plot(HighLow_tmax[[2]],ylim=c(0,30),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation/High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmax$HighLow,col="red",cex=1.4,pch=19)

plot(HighMed_tmax[[2]],ylim=c(0,30),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation/High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmax$HighMed,col="red",pch=19,cex=1.4)

```

```{r}
#### Looking at the differnce
LL_tmax_delta<-Future_mean_Tmax$LowLow-LowLow_tmax[[2]]
LM_tmax_delta<-Future_mean_Tmax$LowMed-LowMed_tmax[[2]]
HL_tmax_delta<-Future_mean_Tmax$HighLow-HighLow_tmax[[2]]
HM_tmax_delta<-Future_mean_Tmax$HighMed-HighMed_tmax[[2]]
```

Here is the change in temperature, all values indicate an increase in the montly mean between the study domain 
and the historic maximum temperature 

```{r,fig.width=10,fig.height=10}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LL_tmax_delta,ylim=c(0,3.5),bty="n",pch=19,
     ylab="Change in Temp",xlab="Month",main="Low Elevation/Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
plot(LM_tmax_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation/Low Latitude")
plot(HL_tmax_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Low Elevatio/High Latitude")
plot(HM_tmax_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation/High Latitude")
```

## If we add the differnce to the study domain temperature, we get the following. 

```{r}
#Modelname="Low_LowElShape_Out"
Monthvec<-HighMed_tmax[[1]]
delta<-LL_tmax_delta
#colnames(MPB_Tmin)
TmaxCreateNewTemp<-function(Monthvec,delta,Modelname){
  Merge<-cbind(Monthvec,delta)
  colnames(Merge)<-c("Month","Delta")
  Merge2<-cbind(MPB_Tmax$Dates,MPB_Tmax$Month,MPB_Tmax[Modelname])
  colnames(Merge2)<-c("Date","Month",Modelname)
  Merged<-merge(Merge,Merge2,by="Month",all.x=T)
  Merged<-Merged[order(Merged$Date),]
  Outputs<-Merged[4]-Merged[2]
  return(list(Merged$Date,as.numeric(Outputs[[1]])))
}
LL_tmax_out<-TmaxCreateNewTemp(Monthvec,LL_tmax_delta,"Low_LowElShape_Out")
LM_tmax_out<-TmaxCreateNewTemp(Monthvec,LL_tmax_delta,"Low_MedElShape_Out")
HL_tmax_out<-TmaxCreateNewTemp(Monthvec,LL_tmax_delta,"High_LowElShape_Out")
HM_tmax_out<-TmaxCreateNewTemp(Monthvec,LL_tmax_delta,"High_MedElShape_Out")
```


```{r,fig.height=10.0,fig.width=10.0}
Dates<-seq(as.Date("2003/10/5"), as.Date("2017/12/31"), "day")
#length(LL_tmax_out[[2]])
#length(Dates)
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(Dates),LL_tmax_out[[2]],ylim=c(-15,40),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation Low Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,)
points(as.Date(Dates),MPB_Tmax$Low_LowElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
plot(as.Date(Dates),LM_tmax_out[[2]],ylim=c(-15,40),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation Low Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0)
points(as.Date(Dates),MPB_Tmax$Low_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
plot(as.Date(Dates),HL_tmax_out[[2]],ylim=c(-15,40),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation High Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,)
points(as.Date(Dates),MPB_Tmax$High_LowElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
plot(as.Date(Dates),HM_tmax_out[[2]],ylim=c(-15,40),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation High Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0)
points(as.Date(Dates),MPB_Tmax$High_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
legend(Dates[3000],40,legend=c("Historic-Adjusted Climate","Modern Climate Driver"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
```

## Minimum Temperature 

```{r,Sorting temperature min files}
Tmin_Files<-list.files(paste0(Drive,"PRISM_tmin_stable_4kmM3_189501_198012_bil/"),
                       pattern="*.bil$")

InputFiles<-Tmin_Files[grep(paste(Years,collapse="|"),Tmin_Files)]
split<-unlist(strsplit(InputFiles,"PRISM_tmin_stable_4kmM3_"))
split<-split[c(F, T)]
Datestring<-unlist(strsplit(split,"_"))
Datestring<-Datestring[c(T,F)]
Year=substr(Datestring,start=1,stop=4)
Month=as.numeric(substr(Datestring,start=5,stop=6))

Prismpath<-paste0(Drive,"PRISM_tmin_stable_4kmM3_189501_198012_bil/")
```

```{r, Proccessing T-Min}

LowLow_tmin=ProcessMeanandVar(Prismpath = Prismpath,LowLow,InputFiles = InputFiles)
HighMed_tmin=ProcessMeanandVar(Prismpath = Prismpath,HighMed,InputFiles = InputFiles)
HighLow_tmin=ProcessMeanandVar(Prismpath = Prismpath,HighLow,InputFiles = InputFiles)
LowMed_tmin=ProcessMeanandVar(Prismpath = Prismpath,LowMed,InputFiles = InputFiles)
```

```{r,Plotting Historic, fig.width=10.0,fig.height=10.0}
# plot(LowLow_tmin[[2]],ylim=c(-15,20))
# points(HighMed_tmin[[2]],col="red")
# points(HighLow_tmin[[2]],col="blue")
# points(LowMed_tmin[[2]],col="green")
```

Proccessing temperature from 2003-2018

```{r}

MPB_Tmin<-read.csv("C:/Users/zacha/Documents/GitHub/IMAP_Python_Project/WPB_Model/WPB_Inputs/MI_Tmin_6_20.csv")
head(MPB_Tmin)
MPB_Tmin$Month<-month(MPB_Tmin$Dates)

Future_mean_Tmin<-aggregate(list(LowLow=MPB_Tmin$Low_LowElShape_Out,
                            LowMed=MPB_Tmin$Low_MedElShape_Out,
                            HighLow=MPB_Tmin$High_LowElShape_Out,
                            HighMed=MPB_Tmin$High_MedElShape_Out),                                             by=list(Month=as.numeric(as.character(MPB_Tmin$Month))),
                       FUN=mean)

Future_Sd<-aggregate(list(LowLow=MPB_Tmin$Low_LowElShape_Out,
                          LowMed=MPB_Tmin$Low_MedElShape_Out,
                          HighLow=MPB_Tmin$High_LowElShape_Out,
                          HighMed=MPB_Tmin$High_MedElShape_Out),
                     by=list(Month=as.numeric(as.character(MPB_Tmin$Month))),
                     FUN=mean)
```


Here is the comparison between the monthly mean between the study domain (2003-2018), and the historic nomral (1895-1945).

```{r,Tmin Past and future, fig.width=10.0,fig.height=10.0}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LowLow_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$LowLow,col="red",cex=1.4,pch=19)

plot(LowMed_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$LowMed,col="red",cex=1.4,pch=19)
legend(1,30,legend=c("Monthly Mean 1895-1945","Monthly Mean 2003-2018"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
plot(HighLow_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$HighLow,col="red",cex=1.4,pch=19)

plot(HighMed_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$HighMed,col="red",pch=19,cex=1.4)

```


```{r}
#### Looking at the differnce
LL_tmin_delta<-Future_mean_Tmin$LowLow-LowLow_tmin[[2]]
LM_tmin_delta<-Future_mean_Tmin$LowMed-LowMed_tmin[[2]]
HL_tmin_delta<-Future_mean_Tmin$HighLow-HighLow_tmin[[2]]
HM_tmin_delta<-Future_mean_Tmin$HighMed-HighMed_tmin[[2]]
```




```{r,fig.width=10,fig.height=10}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LL_tmin_delta,ylim=c(0,3.5),bty="n",pch=19,
     ylab="Change in Temp",xlab="Month",main="Low Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
plot(LM_tmin_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation Low Latitude",)
plot(HL_tmin_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Low Elevation High Latitude")
plot(HM_tmin_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation High Latitude")
```

```{r}
Modelname="Low_LowElShape_Out"
Monthvec<-HighMed_tmin[[1]]
#delta<-LL_tmin_delta
#colnames(MPB_Tmin)
TminCreateNewTemp<-function(Monthvec,delta,Modelname){
  Merge<-cbind(Monthvec,delta)
  colnames(Merge)<-c("Month","Delta")
  Merge2<-cbind(MPB_Tmin$Dates,MPB_Tmin$Month,MPB_Tmin[Modelname])
  colnames(Merge2)<-c("Date","Month",Modelname)
  Merged<-merge(Merge,Merge2,by="Month",all.x=T)
  Merged<-Merged[order(Merged$Date),]
  Outputs<-Merged[4]-Merged[2]
  return(list(Merged$Date,as.numeric(Outputs[[1]])))
}

LL_tmin_out<-TminCreateNewTemp(Monthvec,LL_tmin_delta,"Low_LowElShape_Out")
LM_tmin_out<-TminCreateNewTemp(Monthvec,LM_tmin_delta,"Low_MedElShape_Out")
HL_tmin_out<-TminCreateNewTemp(Monthvec,HL_tmin_delta,"High_LowElShape_Out")
HM_tmin_out<-TminCreateNewTemp(Monthvec,HM_tmin_delta,"High_MedElShape_Out")

```

Here is the adjusted minimum climate driver. 

```{r,fig.height=10.0,fig.width=10.0}
Dates<-seq(as.Date("2001/10/5"), as.Date("2017/12/31"), "day")

par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(Dates),LL_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[1000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation Low Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$Low_LowElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)

plot(as.Date(Dates),LM_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation Low Latitude",xlab="Date",cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$Low_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)

plot(as.Date(Dates),HL_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation High Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$High_LowElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)

plot(as.Date(Dates),HM_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation High Latitude",xlab="Date",cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$High_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
legend(Dates[3000],20,legend=c("Historic-Adjusted Climate","Modern Climate Driver"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
```

```{r,fig.height=10.0,fig.width=10.0}
Dates<-seq(as.Date("2003/10/5"), as.Date("2017/12/31"), "day")

par(mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(Dates),HM_tmin_out[[2]],ylim=c(-25,25),xlim=c(Dates[1000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Coldest WPB Temperatures",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$High_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
abline(h=-17,lty=5,lwd=c(2.0))
abline(h=-22.5,lty=3,lwd=c(2.0))
legend(Dates[2700],25,legend=c("Historic-Adjusted Climate","Modern Climate Driver","Winter Mortality Begins","50 % Mortality Event"),
       pch=c(19,19,NA,NA),col=c("black","red","black"),lty=c(NA,NA,5,3),cex=2.0)
```




### T-Means

```{r,fig.width=10.0,fig.height=10.0}
#### Looking at the differnce


LM_tmean_delta<-((Future_mean_Tmin$LowMed+Future_mean_Tmax$LowMed)/2) -((LowMed_tmax[[2]]+LowMed_tmin[[2]])/2)
LL_tmean_delta<-((Future_mean_Tmin$LowLow+Future_mean_Tmax$LowLow)/2) -((LowLow_tmax[[2]]+LowLow_tmin[[2]])/2)
HM_tmean_delta<-((Future_mean_Tmin$HighLow+Future_mean_Tmax$HighLow)/2) -((HighLow_tmax[[2]]+HighLow_tmin[[2]])/2)
HL_tmean_delta<-((Future_mean_Tmin$HighMed+Future_mean_Tmax$HighMed)/2) -((HighMed_tmax[[2]]+HighMed_tmin[[2]])/2)

par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LL_tmean_delta,ylim=c(0,3.5),bty="n",pch=19,
     ylab="Change in Temp",xlab="Month",main="Low Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
plot(LM_tmean_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation Low Latitude")
plot(HL_tmean_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Low Elevation High Latitude")
plot(HM_tmean_delta,ylim=c(0,3.5),bty="n",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0,
     ylab="Change in Temp",xlab="Month",main="Medium Elevation High Latitude")
```


```{r}
par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(LowLow_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$LowLow,col="red",cex=1.4,pch=19)

plot(LowMed_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$LowMed,col="red",cex=1.4,pch=19)
legend(1,30,legend=c("Monthly Mean 1895-1945","Monthly Mean 2003-2018"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
plot(HighLow_tmin[[2]],ylim=c(-15,15),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(Future_mean_Tmin$HighLow,col="red",cex=1.4,pch=19)

```


```{r,fig.width=10.0,fig.height=10.0}


par(mfrow=c(2,2),mar=c(5.1, 5.1, 4.1, 2.1))
plot(((LowLow_tmax[[2]]+LowLow_tmin[[2]])/2),ylim=c(0,35),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points((Future_mean_Tmin$LowLow+Future_mean_Tmax$LowLow)/2,col="red",cex=1.4,pch=19)
legend(1,35,legend=c("Monthly Mean 1895-1945","Monthly Mean 2001-2018"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
plot(((LowMed_tmax[[2]]+LowMed_tmin[[2]])/2),ylim=c(0,35),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation Low Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(((Future_mean_Tmin$LowMed+Future_mean_Tmax$LowMed)/2),col="red",cex=1.4,pch=19)

plot(((HighLow_tmax[[2]]+HighLow_tmin[[2]])/2),ylim=c(0,35),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Low Elevation High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points((Future_mean_Tmin$HighLow+Future_mean_Tmax$HighLow)/2,col="red",cex=1.4,pch=19)
plot(((HighMed_tmax[[2]]+HighMed_tmin[[2]])/2),ylim=c(0,35),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Medium Elevation High Latitude",
     cex.lab=2.0,cex.axis=2.0,cex=1.4,cex.main=2.0)
points(((Future_mean_Tmin$HighMed+Future_mean_Tmax$HighMed)/2),col="red",cex=1.4,pch=19)
```




```{r,fig.width=10.0,fig.height=10.0}
MeanestOne<-(((LowLow_tmax[[2]]+LowLow_tmin[[2]])/2)+((LowMed_tmax[[2]]+LowMed_tmin[[2]])/2)+((HighLow_tmax[[2]]+HighLow_tmin[[2]])/2)+((HighMed_tmax[[2]]+HighMed_tmin[[2]])/2))/4

MeanestHistory<-(((Future_mean_Tmin$LowLow+Future_mean_Tmax$LowLow)/2)+((Future_mean_Tmin$LowMed+Future_mean_Tmax$LowMed)/2)+((Future_mean_Tmin$HighLow+Future_mean_Tmax$HighLow)/2)+((Future_mean_Tmin$HighMed+Future_mean_Tmax$HighMed)/2))/4


Matrix<-as.data.frame(cbind(MeanestOne,MeanestHistory,c(31,28,31,30,31,30,31,31,30,31,30,31)))
Matrix$daysCurrent<-(Matrix$MeanestOne*Matrix$V3)
Matrix$daysHistoric<-(Matrix$MeanestHistory*Matrix$V3)
Curr<-sum(Matrix$daysCurrent)/365
Hist<-sum(Matrix$daysHistoric)/365
Hist-Curr


57.5/1.37


par(mar=c(5.1, 5.1, 4.1, 2.1))
plot(MeanestOne,ylim=c(0,25),bty="n",pch=19,
     ylab="Temp  (\u00B0C)",xlab="Month",main="Mean Temperature",
     cex.lab=2.0,cex.axis=2.0,cex=2.4,cex.main=2.0)
points(MeanestHistory,col="red",cex=2.4,pch=19)
legend(1,20,legend=c("Monthly Mean 1895-1945","Monthly Mean 2003-2018"),
       pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
```




```{r,fig.width=10.0,fig.height=10.0}

Dates<-seq(as.Date("2003/10/5"), as.Date("2017/12/31"), "day")

par(mar=c(5.1, 5.1, 4.1, 2.1))
plot(as.Date(Dates),LM_tmin_out[[2]],ylim=c(-25,20),xlim=c(Dates[1000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation Low Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,cex.main=2.0)
points(as.Date(Dates),MPB_Tmin$Low_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
abline(h=-15)
# plot(as.Date(Dates),LM_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation Low Latitude",xlab="Date",cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
# points(as.Date(Dates),MPB_Tmin$Low_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
# 
# plot(as.Date(Dates),HL_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Low Elevation High Latitude",xlab="Date",pch=19,cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
# points(as.Date(Dates),MPB_Tmin$High_LowElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
# 
# plot(as.Date(Dates),HM_tmin_out[[2]],ylim=c(-15,20),xlim=c(Dates[3000],Dates[5000]),ylab="Temp  (\u00B0C)",main="Medium Elevation High Latitude",xlab="Date",cex.lab=2.0,cex.axis=2.0,cex=2.0,cex.main=2.0)
# points(as.Date(Dates),MPB_Tmin$High_MedElShape_Out,col=adjustcolor( "red", alpha.f = 0.2),pch=19)
# legend(Dates[3000],20,legend=c("Historic-Adjusted Climate","Modern Climate Driver"),
#        pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
#        pch=c(19,19),col=c("black","red"),cex=c(1.4,1.4))
```
 
```{r}
Tmin_Hist_Out<-data.frame(Dates=LL_tmin_out[[1]],LowerLow=LL_tmin_out[[2]],LowerMed=LM_tmin_out[[2]],
                          UpperLow=HL_tmin_out[[2]],UpperMed=HM_tmin_out[[2]])
                          
write.csv(Tmin_Hist_Out,"Tmin_Historic.csv")

Tmax_Hist_Out<-data.frame(Dates=LL_tmax_out[[1]],LowerLow=LL_tmax_out[[2]],
                          LowerMed=LM_tmax_out[[2]],
                          UpperLow=HL_tmax_out[[2]],UpperMed=HM_tmax_out[[2]])
write.csv(Tmax_Hist_Out,"Tmax_Historic.csv")
```

