---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

### ### Mortality 

This script is used to calculate the FIA conditions for inititating the model and for mortality comparison. 
This model subsets down the FIA data to latitude and elevation parameters for each model within the study area. 
It then calculate percentage of mortality observed during each year. It calculates the inital conditions of the model
from the mean observed ponderosa pine density for the years of 2005-2006. It then applies that percentage of mortality to 
the intial condition for each area for each time step. This results in a csv that was used the MCMC processes and anlaysis. 




```{r}
library(sf)
library(rgdal)
library(plyr)
library(raster)
library(RColorBrewer)
library(dplyr)
options(scipen = 1e8)
Dark2<-brewer.pal(8,'Dark2')
ff<-function(x){
  return(as.numeric(as.character(x)))
}
Pal_1<-brewer.pal(9,"Set3")

'%!in%' <- function(x,y)!('%in%'(x,y))

dft<-function(x){as.data.frame(table(x))}
```

### Getting the Plots Nessecary 

```{r}

###Check for points per raster
Drive<-'C:/Users/zacha/Documents/GitHub/IMAP_Python_Project/'
###Prepare Tree File
Years<-seq(2003,2018)

CA_Tree<-read.csv(paste0(Drive,'Inputs/CA_TREE.csv'))
CA_Tree<-CA_Tree[CA_Tree$INVYR %in% Years,]

##Set projection for project 
proj<-("+init=epsg:4326 +proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Data Location 
FIA_Dir<-paste0(Drive,'Input_Data_Scripts/')
##FIA_Plot location 
CA_Plot<-read.csv(paste0(Drive,'Inputs/CA_PLOT.csv'))
###Remove data without geolocation 
CA_Plot<-CA_Plot[!is.na(CA_Plot$LAT),]
CA_Plot<-CA_Plot[!is.na(CA_Plot$LON),]

###StudyArea to clip to 
SNV_Outline<-readOGR(paste0(Drive,"Inputs/StudyArea/New_Study_Area.shp"))
# #To LAT:LONG
SNV_Outline<-spTransform(SNV_Outline,crs(proj))

#length(unique(CA_Plot$CN))
LL_Points<-cbind(CA_Plot['LON'],CA_Plot['LAT'])
LL_Points<-na.omit(LL_Points)

### Make into spatial points
sp_LL<-sp::SpatialPoints(LL_Points,proj4string = CRS(proj))

## Create the plots as a shape 
DT_sf = sf::st_as_sf(CA_Plot, coords = c("LON", "LAT"), 
                     crs = 4326, agr='constant')
#Do the Intesection
Plots_In_AOI<-sf::st_intersection(sf::st_as_sf(DT_sf),sf::st_as_sf(SNV_Outline))
### Get cordinates back
XYS<-st_coordinates(Plots_In_AOI)

###Check out geospatial locations
par(mar=c(5,5,5,5))
plot(sf::st_geometry(sf::st_as_sf(SNV_Outline)),axes=TRUE)
plot(sf::st_geometry(Plots_In_AOI),cex=.1,add=TRUE,axes=TRUE)

###Number of plots is 3505



### Find  the plots in that are in the area.  Remains at 3504 
Plots<-as.data.frame(CA_Plot[CA_Plot$CN %in% Plots_In_AOI$CN,])

### Get the elevation from each plot in meters
Plots$ELEV_m<-Plots$ELEV*.3408

```



```{r}
#### This function subsets the dataset by the nessecary lat/elevation and sorts out 
#### unnessary species 

SortPlots<-function(one,Sp){
  ### Get the plots in the bounds 
  PltsSorted<-Plots[Plots$ELEV_m>one$LowEl & Plots$ELEV_m<one$HighEl,]
  PltsSorted<-PltsSorted[PltsSorted$LAT>one$LatLow & PltsSorted$LAT<one$LatHigh,]
  ### Subset the database by the plots 
  Subset<-CA_Tree %>%
    ### Get just one plot
    subset(CA_Tree$PLT_CN %in% PltsSorted$CN)%>%  # %>%
    ## Subset to just species of intrest (for now).
    subset(SPCD %in% Sp) %>%
    # ### Get Ht in M
    mutate(DIA_cm= (DIA*2.54))
    colnames(CA_Tree)
  ###Get the nessecary columns
  Subset<-Subset[,c("PLT_CN","INVYR","SPCD","DIA_cm","MORTYR","AGENTCD","TPA_UNADJ","CARBON_AG")]
  hist(Subset$INVYR)
  UPY<-Subset %>%
    ##Group together by the inventory year and the plot number
    group_by(INVYR,PLT_CN)%>%
    ## For each plot number summarize the sum and entires for TPA_UNADJ
    ## This is the total count of stems on the site
    summarise_at(vars("TPA_UNADJ"),list(sum=sum,length=length))
  ### Remove entires with 0 TPA 
  HasTrees<-UPY[!is.na(UPY$sum),]
  ### Resubset by the plots that have trees 
  Relevent_Plots<-Subset[Subset$PLT_CN %in% HasTrees$PLT_CN,]
  return(Subset)
}


#### This calculates the initial population for each study site
CalculateTrees<-function(Subset){

  Subset<-Subset[Subset$INVYR%in%c(2005,2006),]
  All<-Subset[Subset$DIA_cm>10.0,]

  Lrg<-Subset[Subset$DIA_cm>31.8,]
  Smll<-Subset[Subset$DIA_cm< 31.8 & Subset$DIA_cm>10.0,]
  ### Get the years 2005,2006
  ### From this summarise the TPA_UNADJ 
  TPA_All<-All %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("TPA_UNADJ"),list(sum=sum))
  TotalPlots<-length(unique(TPA_All$PLT_CN))
  ###Take the mean and scale form Acre to HA. 
  TPA_Lrg<-Lrg %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("TPA_UNADJ"),list(sum=sum))
  TPA_Smll<-Smll %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("TPA_UNADJ"),list(sum=sum))
  
  (TPA_AllA<-(sum(TPA_All[,3],na.rm = T)*2.47105)/TotalPlots)
  (TPA_LrgA<-(sum(TPA_Lrg[,3],na.rm = T)*2.47105)/TotalPlots)
  (TPA_SmallA<-(sum(TPA_Smll[,3],na.rm = T)*2.47105)/TotalPlots)
  #(length(unique(TPA_1$PLT_CN))))
  ### Return results. 
  return(list(TPA_AllA,TPA_LrgA,TPA_SmallA))}

CalculateCarbon<-function(Subset){

  Subset<-Subset[Subset$INVYR%in%c(2005,2006),]
  All<-Subset[Subset$DIA_cm>10.0,]
  Lrg<-Subset[Subset$DIA_cm>31.8,]
  Smll<-Subset[Subset$DIA_cm< 31.8 & Subset$DIA_cm>10.0,]
  All$Carbon_ACRE<-All$TPA_UNADJ*All$CARBON_AG
  Lrg$Carbon_ACRE<-Lrg$TPA_UNADJ*Lrg$CARBON_AG
  Smll$Carbon_ACRE<-Smll$TPA_UNADJ*Smll$CARBON_AG
  ### Get the years 2005,2006
  ### From this summarise the TPA_UNADJ 
  TPA_All<-All %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("Carbon_ACRE"),list(sum=sum))
  
  TotalPlots<-length(unique(TPA_All$PLT_CN))
  
  ###Take the mean and scale form Acre to HA. 
  TPA_Lrg<-Lrg %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("Carbon_ACRE"),list(sum=sum))
  TPA_Smll<-Smll %>%
    group_by(INVYR,PLT_CN)%>%
    summarise_at(vars("Carbon_ACRE"),list(sum=sum))
  
  (Carbon_AllA<-(sum(TPA_All[,3],na.rm = T)*2.47105*0.453592)/TotalPlots)
  (Carbon_LrgA<-(sum(TPA_Lrg[,3],na.rm = T)*2.47105*0.453592)/TotalPlots)
  (Carbon_SmallA<-(sum(TPA_Smll[,3],na.rm = T)*2.47105*0.453592)/TotalPlots)
  #(length(unique(0TPA_1$PLT_CN))))
  ### Return results. 
  return(list(Carbon_AllA,Carbon_LrgA,Carbon_SmallA))}


Cal_Mort<-function(Subset){
  Relevent_Plots<-Subset
  ### Remove plots that have any of the agent codes for fire, or harvest, vegetation, or unkown. 
  
  
  
  Relevent_Plots$MORTYR[Relevent_Plots$AGENTCD %in% c(20,30,40,60,70,80)]<-NA
  ### Summarize the given mortality year by the tpa_Unadj totaling the number of trees
  MORTYR<-Relevent_Plots %>%
    group_by(year=MORTYR)%>% 
    dplyr::summarise(n=sum(TPA_UNADJ))
  ### Subtract one year for attack year 
  MORTYR$year<-MORTYR$year-1
  ### Get the total trees surveyed in each year
  ALLYR<-Relevent_Plots %>%
    group_by(year=INVYR)%>% 
    dplyr::summarise(n=sum(TPA_UNADJ))
  ### Get the mean 
  ALLYR$mean=mean(ALLYR$n,na.rm=T)
  #ALLYR$Sum=sum(ALLYR$n)
  MortalityTable<-merge(MORTYR,ALLYR,by='year',all.y=T)
  MortalityTable[is.na(MortalityTable)]<-0
  ### Calculate mortality as the number of trees died / trees survyed + Trees died 
  MortalityTable$per<-MortalityTable$n.x/(MortalityTable$mean+MortalityTable$n.x)#(MortalityTable$n.y+MortalityTable$n.x)
  return(MortalityTable)
}

```




### Setting up the analysis


```{r}
## Ponderosa Pine
Sp=122
### Setting up three areas, includes All high latitude and all low latitude for comparitive figures 
### only the 1,2,4,5 entries are used in the analysis. 
PltsLUT<-data.frame(Name=c("UpperLow","UpperMed","HighLatitude","LowerLow","LowerMed","LowLatitude"),
                    Patch=c(1,2,3,4,5,6),
                    LowEl=c(400,1400,400, 400,1500,400),
                    HighEl=c(1400,2000,2000,1500,2200,2200),
                    LatLow=c(37.5,37.5,37.5,33,33,33),
                    LatHigh=c(40,40,40,37.5,37.5,37.5))
```

### Look at the overview

#### All Plots 

##### Number of plots in High Latitude
```{r}

Subset_North<-SortPlots(PltsLUT[3,],Sp)



```

### Number of plots in Low Latitude
```{r}
Subset_South<-SortPlots(PltsLUT[6,],Sp)
```

```{r}
## Complete data set 
Subset_All<-rbind(Subset_North,Subset_South)
OutTrees<-CalculateTrees(Subset_All)
### Run for the whole landscape to compare to Fettig et al., 2019 
All<-Subset_All[ Subset_All$DIA_cm>10.0,]
All<-All[!is.na(All$PLT_CN),]
AllSub<-All[All$INVYR %in% c(2005,2006),]
Mort<-Cal_Mort(All)

```

### Comparing overall mortality to  to Fettig et al., 2019
```{r}
### Fettig feild data
Drive<-'C:/Users/zacha/Documents/GitHub/IMAP_Python_Project/'
FettigData<-read.csv(paste0(Drive,'Inputs/Fettig_Data_Plots.csv'))
## Subset to Ponderosa
Pipo<-FettigData[FettigData$Species=="PIPO",]
Pipo<-Pipo[Pipo$DBH..cm.>10.0,]
# Subset dead
Dead<-Pipo[Pipo$Live.dead=="D",]
### Subset all WPB related causes
WPBs=c("WPB","WPB/MPB","WPB/WIND","WBP","WPB ","WPB/MPB ","WPB/RTB")
WPBKilled<-Dead[Dead$BB.Cause %in% WPBs,]

LrgDeadYear<-table(WPBKilled$Year.death..time.of.attack.or.time.of.injury.other.cause.[WPBKilled$DBH..cm.>31.6])/nrow(Pipo[Pipo$DBH..cm.>31.6,])
SmlDeadYear<-table(WPBKilled$Year.death..time.of.attack.or.time.of.injury.other.cause.[WPBKilled$DBH..cm.<31.6])/nrow(Pipo[Pipo$DBH..cm.<31.6,])
### Aggregated to a percent 
DeadYear<-table(WPBKilled$Year.death..time.of.attack.or.time.of.injury.other.cause.)/nrow(Pipo)
```

```{r}

#### Plotting the comparison 
All<-Subset_All[ Subset_All$DIA_cm>10.0,]
All<-All[!is.na(All$PLT_CN),]
AllSub<-All[All$INVYR %in% c(2005,2006),]
Mort<-Cal_Mort(All)
bar<-barplot(Mort[[5]]*100,names.arg=Mort[[1]],main="Percent Mortality Western Pine Beetle >10. cm",
        ylab="Percent of Mortality",cex.main=1.5,cex.lab=1.2,cex.axis=1.2,ylim=c(0,60))
points(bar[12:15],DeadYear*100,cex=1.20,col="red",pch=19)
legend(1,50,legend=c("Fettig et al., 2019"),cex=1.2,col="red",pch=19)

```


```{r}
#### Plotting the comparison 
Lrg<-Subset_All[Subset_All$DIA_cm>31.8,]
LrgSub<-Lrg[Lrg$INVYR %in% c(2005,2006),]
LrgMort<-Cal_Mort(Lrg)
bar<-barplot(LrgMort[[5]][1:15]*100,names.arg=LrgMort[[1]][1:15],main="Percent Mortality Western Pine Beetle >31.8 cm",
        ylab="% Mortality",cex.main=1.5,cex.lab=1.2,cex.axis=1.2,ylim=c(0,60))
points(bar[12:15],c(LrgDeadYear*100,0),cex=1.2,col="red",pch=19)
legend(1,50,legend=c("Fettig et al., 2019"),cex=1.0,col="red",pch=19)
sum(LrgMort$per,na.rm=T)

```

```{r}
#### Plotting the comparison 
Smll<-Subset_All[Subset_All$DIA_cm< 31.8& Subset_All$DIA_cm>10.0,]
Smll<-Smll[!is.na(Smll$PLT_CN),]
SmllSub<-Smll[Smll$INVYR %in% c(2005,2006),]
SmllMort<-Cal_Mort(Smll)
barplot(SmllMort[[5]]*100,names.arg=SmllMort[[1]],main="Percent Mortality Western Pine Beetle < 31.8 cm",
        ylab="% Mortality",cex.main=1.5,cex.lab=1.2,cex.axis=1.2,ylim=c(0,35))
points(bar[12:15],SmlDeadYear*100,cex=1.20,col="red",pch=19)
sum(LrgMort$per,na.rm=T)
sum(SmllMort$per,na.rm=T)
Output<-cbind(SmllMort[[1]],Mort[[5]],SmllMort[[5]],LrgMort[[5]])
legend(1,25,legend=c("Fettig et al., 2019"),cex=1.2,col="red",pch=19)

```


#### Calculate out the mortality for each site for each time step. 

```{r}
DF<-NULL
DF2<-NULL
DF3<-NULL
#one<-PltsLUT[1,]

for(i in c(1,2,4,5)){
  print(paste0("########### Plot ",i,"  ###################"))
  Subset<-SortPlots(PltsLUT[i,],Sp)
  Trees<-CalculateTrees(Subset)
  Carbonlist<-CalculateCarbon(Subset)
  Lrg<-Subset[Subset$DIA_cm >31.6,]
  #LrgSub<-Lrg[Lrg$INVYR %in% c(2005,2006),]
  Mortlrg<-Cal_Mort(Lrg)
  Mortlrg<-Mortlrg[Mortlrg$year %in% seq(2006,2018),]
  MortlrgPass<-data.frame(year= seq(2006,2018))
  MortlrgPass<-merge(MortlrgPass,Mortlrg,by="year",all.x=T)
  Mortlrg<-MortlrgPass
  Mortlrg$per[is.na(Mortlrg$per)]<-0
  plot(Mortlrg[[5]],main=paste0("Large Mortality Site ", i ))
  
  Smll<-Subset[Subset$DIA_cm < 31.6 & Subset$DIA_cm > 10.0,]
  Smll<-Smll[!is.na(Smll$PLT_CN),]
  Mortsmll<-Cal_Mort(Smll)
  Mortsmll<-Mortsmll[Mortsmll$year %in% seq(2006,2018),]
  MortsmllPass<-data.frame(year= seq(2006,2018))
  MortsmllPass<-merge(MortsmllPass,Mortsmll,by="year",all.x=T)
  Mortsmll<-MortsmllPass
  Mortsmll$per[is.na(Mortsmll$per)]<-0
  plot(Mortsmll[[5]],main=paste0("Small Mortality Site ", i ))
  Lrgtree<-Trees[[2]]
  Smlltree<-Trees[[3]]
  Mrs<-0
  Mrl<-0
  for(j in 1:13){
    #print(Ml)
    #print(Mortlrg[[1]][j])
    Ms<-Mortsmll[[5]][j]
    #print(Ms)
    Ml<-Mortlrg[[5]][j]
    #print(Ml)
    Smlltree<-c(Smlltree,Smlltree[j]-Smlltree[1]*Ms)
    Lrgtree<-c(Lrgtree,Lrgtree[j]-Lrgtree[1]*Ml)
    Mrs<-c(Mrs,Ms)
    Mrl<-c(Mrl,Ml)
    
    
    
    
  }
  Row<-c(PltsLUT[i,1],Lrgtree,Smlltree)
  DF<-rbind(Row,DF)
  Row2<-c(PltsLUT[i,1],Mrs,Mrl)
  DF2<-rbind(Row2,DF2)
  Row3<-c(PltsLUT[i,1],unlist(Carbonlist[1]),unlist(Carbonlist[2]),unlist(Carbonlist[3]))
  DF3<-rbind(Row3,DF3)
}
write.csv(DF3,"Carbonpersite.csv")
```




```{r}
### Recombine as one dataframe 
DF2[is.na(DF2)]<-0
DF[is.na(DF)]<-0
DF_Out<-as.data.frame(DF)
colnames(DF_Out)<-c("Location","Initial_above_20","Large2006Perc","Large2007Perc","Large2008perc","Large2009perc",
                    "Large2010perc","Large2011perc","Large2012perc","Large2013perc",
                    "Large2014perc","Large2015perc",
                    "Large2016perc","Large2017perc","Large20018Perc","Initial_below_20",
                    "Small2006perc","Small2007perc","Small2008perc","Small2009perc",
                    "Small2010perc","Small2011perc","Small2012perc","Small2013perc",
                    "Small2014perc","Small2015perc","Small2016perc","Small2017perc","Small2018perc")

colnames(DF_Out)
DF_Out2<-DF_Out[,c(1,2,16,3:15,17:29)]


```


### Here is Mortality Plotted Out


```{r,fig.width=10.0,fig.height=10.0}
### Plotters 
library(RColorBrewer)
Dark2<-brewer.pal(6,"Dark2")
#colnames(MPB3)
MPB3_plotter<-as.data.frame(DF_Out[,c(1:15)])
MPB3_plotter<-t(MPB3_plotter)
colnames(MPB3_plotter)<-MPB3_plotter[1,]
MPB3_plotter<-MPB3_plotter[-1,]
fix<-function(x){
  as.numeric(as.character(x))
}

Dates<-seq(
  from=as.POSIXct("2005-06-01 0:00", tz="UTC"),
  to=as.POSIXct("2018-06-01 0:00", tz="UTC"),
  by="year"
)  
#MPB3_plotter$Dates<-Dates

plot(MPB3_plotter[,1],ylim=c(0,60),xaxt='n',main="WPB Host(>31.6 cm) Tree Density Over Time",ylab="Tree Density Per Ha",xlab="Date",type="l",cex=1.5,cex.axis=1.5,cex.lab=1.5,lwd=3.0)
axis(1, at=1:14,labels =Dates, las=1,cex.axis=1.0,pch=15,cex=1.5,cex.axis=1.5,cex.lab=2.0)
##points(MPB3_plotter[,2],pch=16,col=Dark2[1],cex=1.5)
lines(MPB3_plotter[,2],lty=1,col=Dark2[2],cex=1.5,lwd=3.0)
#points(MPB3_plotter[,4],pch=18,col=Dark2[3],cex=1.5)
lines(MPB3_plotter[,3],lty=1,col=Dark2[4],cex=1.5,lwd=3.0)
lines(MPB3_plotter[,4],lty=1,col=Dark2[5],cex=1.5,lwd=3.0)
legend(9.0,50,legend=c("LowLat_HE","LowLat_LE","HighLat_HE","HighLat_LE"),cex=1.5,pch=c(15,15,15,15),col=c("Black",Dark2[2],Dark2[4],Dark2[5]))





plot(fix(MPB3_plotter[,1])/max(fix(MPB3_plotter[,1])),type="l",ylim=c(0,1.2),main="WPB Host(> 31.6 cm) Population remaining",xaxt='n',xlab="Date",ylab="Intial population remaining",cex=1.5,cex.axis=1.5,cex.lab=1.5,lwd=3.0)
axis(1, at=1:14,labels =Dates, las=1,cex=1.5,cex.axis=1.5,cex.lab=1.5)
#points(fix(MPB3_plotter[,2])/fix(max(MPB3_plotter[,2])),pch=16,col=Dark2[1],cex=1.5)
lines(fix(MPB3_plotter[,2])/max(fix(MPB3_plotter[,2])),pch=15,col=Dark2[2],cex=1.5,lwd=3.0)
#points(fix(MPB3_plotter[,4])/fix(max(MPB3_plotter[,4])),pch=18,col=Dark2[3],cex=1.5)
lines(fix(MPB3_plotter[,3])/max(fix(MPB3_plotter[,3])),pch=15,col=Dark2[3],cex=1.5,lwd=3.0)
lines(fix(MPB3_plotter[,4])/max(fix(MPB3_plotter[,4])),pch=15,col=Dark2[5],cex=1.5,lwd=3.0)
legend(1.2,.5,legend=c("LowLat_HE","LowLat_LE","HighLat_HE","HighLat_LE"),cex=1.5,pch=c(15,15,15,15),col=c("Black",Dark2[2],Dark2[3],Dark2[5]))



```



```{r,fig.width=10.0,fig.height=10.0}



MPB3_plotter<-as.data.frame(DF_Out[,c(1,16:29)])
MPB3_plotter<-t(MPB3_plotter)
colnames(MPB3_plotter)<-MPB3_plotter[1,]
MPB3_plotter<-MPB3_plotter[-1,]
fix<-function(x){
  as.numeric(as.character(x))
}

Dates<-seq(
  from=as.POSIXct("2007-01-01 0:00", tz="UTC"),
  to=as.POSIXct("2017-01-01 0:00", tz="UTC"),
  by="year"
)  

plot(MPB3_plotter[,1],ylim=c(0,80),xaxt='n',main="WPB Host(<31.6 cm) Tree Density Over Time",ylab="Tree Density Per Ha",xlab="Date",type="l",cex=1.5,cex.axis=1.5,cex.lab=1.5,lwd=3.0)
axis(1, at=1:11,labels =Dates, las=1,cex.axis=1.0,pch=15,cex=1.5,cex.axis=1.5,cex.lab=2.0)
##points(MPB3_plotter[,2],pch=16,col=Dark2[1],cex=1.5)
lines(MPB3_plotter[,2],lty=1,col=Dark2[2],cex=1.5,lwd=3.0)
#points(MPB3_plotter[,4],pch=18,col=Dark2[3],cex=1.5)
lines(MPB3_plotter[,3],lty=1,col=Dark2[4],cex=1.5,lwd=3.0)
lines(MPB3_plotter[,4],lty=1,col=Dark2[5],cex=1.5,lwd=3.0)
legend(9.0,300,legend=c("LowLat_HE","LowLat_LE","HighLat_HE","HighLat_LE"),cex=1.5,pch=c(15,15,15,15),col=c("Black",Dark2[2],Dark2[4],Dark2[5]))





plot(fix(MPB3_plotter[,1])/max(fix(MPB3_plotter[,1])),type="l",ylim=c(0,1.2),main="WPB Host(<31.6 cm) Population remaining",xaxt='n',xlab="Date",ylab="Intial population remaining",cex=1.5,cex.axis=1.5,cex.lab=1.5,lwd=3.0)
axis(1, at=1:11,labels =Dates, las=1,cex=1.5,cex.axis=1.5,cex.lab=1.5)
#points(fix(MPB3_plotter[,2])/fix(max(MPB3_plotter[,2])),pch=16,col=Dark2[1],cex=1.5)
lines(fix(MPB3_plotter[,2])/max(fix(MPB3_plotter[,2])),pch=15,col=Dark2[2],cex=1.5,lwd=3.0)
#points(fix(MPB3_plotter[,4])/fix(max(MPB3_plotter[,4])),pch=18,col=Dark2[3],cex=1.5)
lines(fix(MPB3_plotter[,3])/max(fix(MPB3_plotter[,3])),pch=15,col=Dark2[4],cex=1.5,lwd=3.0)
lines(fix(MPB3_plotter[,4])/max(fix(MPB3_plotter[,4])),pch=15,col=Dark2[5],cex=1.5,lwd=3.0)
legend(1.2,.5,legend=c("LowLat_HE","LowLat_LE","HighLat_HE","HighLat_LE"),cex=1.5,pch=c(15,15,15,15),col=c("Black",Dark2[2],Dark2[4],Dark2[5]))


```

```{r}
DF_Out<-as.data.frame(DF)
DF[is.na(DF)]<-0
DF_Out<-as.data.frame(DF)
colnames(DF_Out)<-c("Location","Initial_above_20","Large2006Perc","Large2007Perc","Large2008perc","Large2009perc",
                    "Large2010perc","Large2011perc","Large2012perc","Large2013perc",
                    "Large2014perc","Large2015perc",
                    "Large2016perc","Large2017perc","Large20018Perc","Initial_below_20",
                    "Small2006perc","Small2007perc","Small2008perc","Small2009perc",
                    "Small2010perc","Small2011perc","Small2012perc","Small2013perc",
                    "Small2014perc","Small2015perc","Small2016perc","Small2017perc","Small2018perc")

colnames(DF_Out)
DF_Out2<-DF_Out[,c(1,2,16,3:15,17:29)]


### Open this writer when you want to to print the csv
#write.csv(DF_Out2,paste0(Drive,"/WPB_Model/WPB_Inputs/WPB_Trees_6_20.csv"))
```



#### Extra

#### Mortality at the two elevations.

```{r}
#Low_Elevation
LE1<-SortPlots(PltsLUT[1,],Sp)
LE2<-SortPlots(PltsLUT[4,],Sp)
Subset_All<-rbind(LE2,LE1)
OutTrees<-CalculateTrees(Subset_All)
print(OutTrees[[1]])
print(OutTrees[[2]])
print(OutTrees[[3]])

All<-Subset_All[ Subset_All$DIA_cm>10.0,]
All<-All[!is.na(All$PLT_CN),]
AllSub<-All[All$INVYR %in% c(2005,2006),]
MortLE<-Cal_Mort(All)
# barplot(MortLE[[5]],names.arg=Mort[[1]],main="Percent Mortality Western Pine Beetle >10. cm",
#         ylab="% Mortality",cex.main=1.5,cex.lab=1.2,cex.axis=1.2)
# sum(Mort$per)
```

```{r}
HE1<-SortPlots(PltsLUT[2,],Sp)
HE2<-SortPlots(PltsLUT[5,],Sp)
Subset_All<-rbind(HE2,HE1)
OutTrees<-CalculateTrees(Subset_All)
print(OutTrees[[1]])
print(OutTrees[[2]])
print(OutTrees[[3]])

All<-Subset_All[ Subset_All$DIA_cm>10.0,]
All<-All[!is.na(All$PLT_CN),]
AllSub<-All[All$INVYR %in% c(2005,2006),]
MortHE<-Cal_Mort(All)
# barplot(MortHE[[5]],names.arg=Mort[[1]],main="Percent Mortality Western Pine Beetle >10. cm",
#         ylab="% Mortality",cex.main=1.5,cex.lab=1.2,cex.axis=1.2)
# sum(Mort$per)
```
```{r,fig.width=20.0,fig.height=10.0}
MortHE$EL<-"High"
MortLE$EL<-"Low"
Mortall<-rbind(MortHE,MortLE)
Mortall<-Mortall[,c(-2,-3,-4)]
#Mortall

d <- data.frame(row.names=seq(2003,2018), High_Elevation =MortHE$per*100, 
                Low_Elevation = MortLE$per*100)
d<-do.call(rbind,d)
#tab<-reshape2::melt(Mortall,id.vars=c("year","EL"))
#?melt
par(mar=c(7,7,7,5),xpd=F)
barplot(d,beside=T,names.arg=MortHE$year, legend.text = rownames(d), 
        args.legend = list(x = "topleft", bty="n",cex= 3),ylab="Percent Mortality",
        main="Western Pine Beetle Mortality",cex=3.0,cex.main=5.0,cex.lab=3.0,cex.axis=3.0
        )
```

