---
title: "Phloem Temp"
author: "Zjrobbin"
date: "8/11/2020"
output: html_document
---


### Data

Here is the data from Jim Powell
It is four trees North South,a bark surface temperature, and the ambient air. 
Measured every hour for ~ 1 year

```{r setup, include=FALSE}
library(dplyr)
setwd("C:/Users/zacha/Documents/GitHub/IMAP_Python_Project/WPB_Model/Supplemental/NewPhleom/")

PonderosaData<-read.csv("ponderosapinephloem.csv")
head(PonderosaData)
```

I started by reducing North South to a single tree, and toook the mean of all 
trees.

```{r cars}

PonderosaTrunc<-data.frame(Tree1=(PonderosaData$T1N+PonderosaData$T1S)/2,
                           Tree2=(PonderosaData$T2N+PonderosaData$T2S)/2,
                           Tree3=(PonderosaData$T3N+PonderosaData$T3S)/2,
                           Tree4=(PonderosaData$T4N+PonderosaData$T4S)/2,
                           AirTemp=PonderosaData$Air)


PonderosaTrunc$meanT<-(PonderosaTrunc$Tree1+PonderosaTrunc$Tree2+PonderosaTrunc$Tree3+PonderosaTrunc$Tree4)/4

```


Here I clean up the date structure
```{r}
PonderosaTrunc$Day<-PonderosaData$JD
PonderosaTrunc$Year<-PonderosaData$Year
PonderosaTrunc$Hour<-PonderosaData$Time

###Missing Data
PonderosaTrunc<-PonderosaTrunc[c(-8073),]
PonderosaTrunc$Day[PonderosaTrunc$Year=="1995"]<-PonderosaTrunc$Day[PonderosaTrunc$Year=="1995"]+365
PonderosaTrunc$Date<-as.Date(PonderosaTrunc$Day-1,origin = "1994-01-01")
```

Took the daily mean 

```{r}
DayAir<-PonderosaTrunc %>%
  group_by(Date=Date) %>%
  summarise(Max=max(AirTemp),Min=min(AirTemp))
```

I wanted to look at the best way to orient the sin wave So I looked at the 
best combination of a times to capture the min and max I decided on 4 am 
4 pm to be the apex and low


```{r,fig.width=14,fig.height=7}
DayAir<-PonderosaTrunc %>%
  group_by(Date=Date) %>%
  summarise(Max=max(AirTemp),Min=min(AirTemp))

HourlyAir<-PonderosaTrunc %>%
  group_by(Date=Hour) %>%
  summarise(Max=max(AirTemp),Min=min(AirTemp),Mean=mean(AirTemp))
par(mar=c(5,5,5,20),xpd=F)
plot(HourlyAir$Max,col="red",ylim=c(-30,30),xlab="Hour",ylab="Temperature (\u00B0C)",main="Hourly Temperature Ranges",pch=19,cex=1.6,cex.main=2.0,
     cex.axis=1.6,cex.lab=1.6)
points(HourlyAir$Min,col="blue",pch=19,cex=1.6)
points(HourlyAir$Mean,pch=19,cex=1.6)
abline(v=4)
#abline(v=7,lty=2)
#abline(v=10,lty=2)
#abline(v=13,lty=2)
abline(v=16)
par(xpd = T)
legend(26,0,legend=c("Maximum Temperature","Mean Temperature","Minimum Temperature"),pch=c(19,19,19),
       col=c("red","black","blue"),cex=1.6)
#abline(v=19,lty=2)
#abline(v=22,lty=2)
```
This is the max mean and min.

This function sin-adjust the minimum and maximum into 8 segments  
It this one returns a data frame with each hours


```{r}

Tmax<-DayAir$Max
Tmin<-DayAir$Min
vector<-NULL
for(i in 1:length(Tmax)-1){
  Min<-Tmin[i]
  Max<-Tmax[i]
  Min2<-Tmin[i+1]
  Mean=(Max+Min)/2
  Mean2=(Max+Min2)/2
  Dif=(Max-Min)
  Dif2=(Max-Min2)
  Fouram<-Min
  Sevenam<-Mean+(.5*Dif*sin(-pi/4))
  Tenam<-Mean+(.5*Dif*sin(0))
  Onepm<-Mean+(.5*Dif*sin(pi/4))
  Fourpm<-Mean+(.5*Dif*sin(pi/2))
  Sevenpm<-Mean2+(.5*Dif2*sin(pi/4))
  Tenpm<-Mean2+(.5*Dif2*sin(0))
  OneAm<-Mean2+(.5*Dif2*sin(-pi/4))
  
  
  if(i==1){vector<-cbind(Fouram,Sevenam,Tenam,Onepm,Fourpm,Sevenpm,Tenpm,OneAm)}
  else{vector<-rbind(vector,cbind(Fouram,Sevenam,Tenam,Onepm,Fourpm,Sevenpm,Tenpm,OneAm))}
}
SimData<-as.data.frame(vector)
```

I then fit a linear phloem adjustment to each hour, to account for the buffering of the bark 

```{r,fig.width=10.0,fig.height=10.0}
#### Four Am
par(pty="s")
FourAMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="400"]
lm1<-lm(FourAMphl~SimData$Fouram[1:386])
plot(FourAMphl,3.8532+(.9677*SimData$Fouram[1:386]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
summary(lm1)
text(-10, 10, "B0=3.8532, B1=.9677,R2=.9328", pos = 4)

```


```{r,fig.width=10.0,fig.height=10.0}
SevenAMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="700"]
lm2<-lm(SevenAMphl~SimData$Sevenam[1:386])
plot(SevenAMphl,1.86978+(.93522*SimData$Sevenam[1:386]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
summary(lm2)
text(-10, 10, "B0=1.86978, B1=.93522,R2=0.9459", pos = 4)
```

```{r,fig.width=10.0,fig.height=10.0}
###3
TenAMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="1000"]
lm3<-lm(TenAMphl~SimData$Tenam[1:388])
summary(lm3)

plot(TenAMphl,-.45333+(1.00899*SimData$Tenam[1:388]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 10, "B0=-.45333, B1=1.00899,R2=.9269", pos = 4)

```

```{r,fig.width=10.0,fig.height=10.0}

### One PM (4)

OnePMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="1300"]
lm4<-lm(OnePMphl~SimData$Onepm[1:387])
summary(lm4)

plot(OnePMphl,-1.148846 +(0.985801*SimData$Onepm[1:387]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 20, "B0=-1.148846, B1=0.985801,R2=.9665", pos = 4)
```

```{r,fig.width=10.0,fig.height=10.0}
### Four Pm (5)
FourPMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="1600"]
lm5<-lm(FourPMphl~SimData$Fourpm[1:386])
summary(lm5)

plot(FourPMphl,0.065686 +(0.942395*SimData$Fourpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 20, "B0=0.065686, B1=0.942395,R2=.9612", pos = 4)

```

```{r,fig.width=10.0,fig.height=10.0}
### Seven Pm (6)
SevenPMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="1900"]
lm6<-lm(SevenPMphl~SimData$Sevenpm[1:386])
summary(lm6)


plot(SevenPMphl,-0.54496 +(0.96128*SimData$Sevenpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 20, "B0=-0.54496, B1=0.96128,R2=.9686", pos = 4)

```


```{r,fig.width=10.0,fig.height=10.0}

#### Ten Pm
TenPMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="2200"]
lm7<-lm(TenPMphl~SimData$Tenpm[1:386])
summary(lm7)

plot(TenPMphl,0.934665 +(0.988126*SimData$Tenpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 20, "B0=0.934665 , B1=0.988126,R2=0.9645", pos = 4)

```

```{r,fig.width=10.0,fig.height=10.0}
#### One Am (8)
par(pty="s")
OneAMphl<-PonderosaTrunc$meanT[PonderosaTrunc$Hour=="100"]
lm8<-lm(OneAMphl~SimData$OneAm[1:386])
summary(lm8)

plot(OneAMphl,3.18995 +(1.005804*SimData$OneAm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Obsevered Phloem Temps"))
abline(1,1)
text(-10, 20, "B0= 3.18995 , B1=1.005804,R2=0.9442", pos = 4)

```


```{r,fig.width=7.0,fig.height=14.0}

png("HourlySin.png", units="in", width=7.0, height=14.0, res=500)
par(mfrow=c(4,2),pty="s")
plot(FourAMphl,3.8532+(.9677*SimData$Fouram[1:386]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="4:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)

text(-15, 24, "B0 = 3.85", pos = 4,cex=1.5)
text(-15, 20,  "B1 = 0.97",  pos = 4,cex=1.5)
text(-15, 16, as.expression(bquote(italic(R)^2 == .(format( 0.93, digits = 2)))), pos = 4,cex=1.5)

plot(SevenAMphl,1.86978+(.93522*SimData$Sevenam[1:386]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="7:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)

text(-15, 24, "B0 = 1.90", pos = 4,cex=1.5)
text(-15, 20,  "B1 = 0.94",  pos = 4,cex=1.5)
text(-15, 16, as.expression(bquote(italic(R)^2 == .(format( 0.95, digits = 2)))), pos = 4,cex=1.5)

plot(TenAMphl,-.45333+(1.00899*SimData$Tenam[1:388]),xlim=c(-15,25),ylim=c(-15,25),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="10:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)

text(-15, 24, "B0 = -0.45", pos = 4,cex=1.5)
text(-15, 20,  "B1 = 1.01",  pos = 4,cex=1.5)
text(-15, 16, as.expression(bquote(italic(R)^2 == .(format( 0.93, digits = 2)))), pos = 4,cex=1.5)

plot(OnePMphl,-1.148846 +(0.985801*SimData$Onepm[1:387]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="13:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)
#text(-13, 34, "B0=-1.148846, B1=0.985801, R2=.9665", pos = 4,cex=1.0)

text(-10, 30, "B0 = -1.15", pos = 4,cex=1.5)
text(-10, 26,  "B1 = 0.99",  pos = 4,cex=1.5)
text(-10, 22, as.expression(bquote(italic(R)^2 == .(format( 0.97, digits = 2)))), pos = 4,cex=1.5)

plot(FourPMphl,0.065686 +(0.942395*SimData$Fourpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="16:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)
text(-10, 30, "B0 = 0.07", pos = 4,cex=1.5)
text(-10, 26,  "B1 = 0.94",  pos = 4,cex=1.5)
text(-10, 22, as.expression(bquote(italic(R)^2 == .(format( 0.96, digits = 2)))), pos = 4,cex=1.5)


plot(SevenPMphl,-0.54496 +(0.96128*SimData$Sevenpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="19:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)


text(-10, 30, "B0 = -0.54", pos = 4,cex=1.5)
text(-10, 26,  "B1 = 0.96",  pos = 4,cex=1.5)
text(-10, 22, as.expression(bquote(italic(R)^2 == .(format( 0.97, digits = 2)))), pos = 4,cex=1.5)


plot(TenPMphl,0.934665 +(0.988126*SimData$Tenpm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="22:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)
#text(-13, 34, "B0=0.934665, B1=0.988126, R2=0.9645", pos = 4,cex=1.0)
text(-10, 30, "B0 = -0.93", pos = 4,cex=1.5)
text(-10, 26,  "B1 = 0.98",  pos = 4,cex=1.5)
text(-10, 22, as.expression(bquote(italic(R)^2 == .(format( 0.96, digits = 2)))), pos = 4,cex=1.5)

plot(OneAMphl,3.18995 +(1.005804*SimData$OneAm[1:386]),xlim=c(-10,35),ylim=c(-10,35),ylab=c("Modeled Response"),xlab=c("Observed Phloem Temps"),pch=19,
     col=adjustcolor("black",alpha.f = .2),main="1:00",cex.axis=2.0,cex.lab=2.0,cex.main=2.0)
abline(1,1,lwd=2.0)
#text(-13, 34, "B0= 3.18995, B1=1.005804, R2=0.9442", pos = 4,cex=1.0)

text(-10, 30, "B0 = 3.19", pos = 4,cex=1.5)
text(-10, 26,  "B1 = 1.01",  pos = 4,cex=1.5)
text(-10, 22, as.expression(bquote(italic(R)^2 == .(format( 0.94, digits = 2)))), pos = 4,cex=1.5)
dev.off()
```


So once I fit those I then looked at what the whole data set would look like.
This is the same sin curve fitting method as before, except now we are using the
adjustment for the phloem 

```{r}
####Comparing the whole thing 

Tmax<-DayAir$Max
Tmin<-DayAir$Min
Fittedvector<-NULL
for(i in 1:length(Tmax)-1){
  Min<-Tmin[i]
  Max<-Tmax[i]
  Min2<-Tmin[i+1]
  Mean=(Max+Min)/2
  Mean2=(Max+Min2)/2
  Dif=(Max-Min)
  Dif2=(Max-Min2)
  Fouram<-as.numeric(lm1$coefficients[1]+lm1$coefficients[2]*(Min))
  Sevenam<-as.numeric(lm2$coefficients[1]+lm2$coefficients[2]*(Mean+(.5*Dif*sin(-pi/4))))
  Tenam<-as.numeric(lm3$coefficients[1]+lm3$coefficients[2]*(Mean+(.5*Dif*sin(0))))
  Onepm<-as.numeric(lm4$coefficients[1]+lm4$coefficients[2]*(Mean+(.5*Dif*sin(pi/4))))
  Fourpm<-as.numeric(lm5$coefficients[1]+lm5$coefficients[2]*(Mean+(.5*Dif*sin(pi/2))))
  Sevenpm<-as.numeric(lm6$coefficients[1]+lm6$coefficients[2]*(Mean2+(.5*Dif2*sin(pi/4))))
  Tenpm<-as.numeric(lm7$coefficients[1]+lm7$coefficients[2]*(Mean2+(.5*Dif2*sin(0))))
  OneAm<-as.numeric(lm8$coefficients[1]+lm8$coefficients[2]*(Mean2+(.5*Dif2*sin(-pi/4))))
  
  
  if(i==1){Fittedvector<-c(Fouram,Sevenam,Tenam,Onepm,Fourpm,Sevenpm,Tenpm,OneAm)}
  else{Fittedvector<-c(Fittedvector,c(Fouram,Sevenam,Tenam,Onepm,Fourpm,Sevenpm,Tenpm,OneAm))}
}

```

Then I reconstruct the phloem data for the hours we are modeling 

```{r}

#plot(Fittedvector,ylim=c(0,30))
#plot(PonderosaTrunc$meanT,ylim=c(0,30))

for(i in 1:length(FourAMphl)){

if(i==1){Obs<-c(FourAMphl[i],SevenAMphl[i],TenAMphl[i],OnePMphl[i],
                FourPMphl[i],SevenPMphl[i],TenPMphl[i],OneAMphl[i])  }
else{Obs<-c(Obs,c(FourAMphl[i],SevenAMphl[i],TenAMphl[i],OnePMphl[i],
                             FourPMphl[i],SevenPMphl[i],TenPMphl[i],OneAMphl[i]))}
}
```


```{r,fig.width=10.0,fig.height=10.0}
Fit<-Fittedvector[1:3088]
plot(Obs,Fit)
abline(1,1)
```

```{r,fig.width=20.0,fig.height=10.0}
library(grDevices)

summary(lm(Obs~Fit))
#png("PhloemModelcomp.png", units="in", width=20.0, height=10.0, res=300)
par(mar=c(7,7,5,5))
Days<-rep(DayAir$Date,each=8)
head(Days)
plot(as.Date(as.character(Days[1:3088])),Obs,col=adjustcolor("red",alpha.f = .5),xlab=NA,pch=16,xaxt='n',ylab=NA,
     cex.lab=2.4,cex.axis=3.0)

#axis.Date(1, at=c(Days[1],Days[1000],Days[2000],Days[3000]), labels=c(Days[1],Days[1000],Days[2000],Days[3000]), cex.lab=2.4,cex.axis=2.4)
text(as.Date(as.character(Days[1175])), 18, as.expression(bquote(italic(R)^2 == .(format( 0.96, digits = 2)))), pos = 4,cex=3.0)
axis.Date(1,at=seq(as.Date(Days)[1], as.Date(Days)[3104],by="month"),format=c('%m-%Y'),line=1.0,
     font.lab=3.0,col=NA, cex.lab=3.0,cex.axis=3.0)
title(xlab="Date", cex.lab=2.4,line=5.0)
title(ylab=("Temperature (\u00B0C)"), cex.lab=2.4,line=5.0)
points(as.Date(as.character(Days[1:3088])),Fit,col=adjustcolor("black",alpha.f = .5),pch=16,type="l",lwd=1.5)
legend(as.Date(as.character(Days[1200])),30,legend=c("Modeled Temperature","Observed Temperature"),col=c(adjustcolor("black",alpha.f = .5),adjustcolor("red",alpha.f = .5)),pch=c(NA,19),lty=c(1,NA),cex=2.4)
#dev.off()

```


To look at total data capture I repeat each meausrement to get to an hourly level. 

```{r,fig.width=10.0,fig.height=10.0}
RepeatedFit<-rep(Fit,each=3)
MeanPheolm<-PonderosaTrunc$meanT[1:9264]
plot(RepeatedFit,MeanPheolm,col=adjustcolor("red",alpha.f = .1))
abline(1,1)

```



```{r}
plot(RepeatedFit-MeanPheolm,col=adjustcolor("red",alpha.f = .1))
```
```{r}

```


Heres how the original trees would compare

```{r,fig.width=10.0,fig.height=10.0}

png("Phloem4YTrees.png", units="in", width=10.0, height=10.0, res=300)
par(mfrow=c(2,2),mar=c(5,5,3,3))
Tree1<-PonderosaTrunc$Tree1[1:9264]
plot(RepeatedFit,Tree1,col=adjustcolor("black",alpha.f = .05),pch=19,xlab="Hourly Phloem Measurement",ylab="Modeled Hourly Temperature",
     main="Ponderosa Pine 1",cex=1.2,cex.main=2.0,cex.lab=1.5,cex.axis=2.0)
abline(1,1,lwd=3.0)

Tree2<-PonderosaTrunc$Tree2[1:9264]
plot(RepeatedFit,Tree2,col=adjustcolor("black",alpha.f = .05),pch=19,xlab="Hourly Phloem Measurement",ylab="Modeled Hourly Temperature",
     main="Ponderosa Pine 2",cex=1.2,cex.main=2.0,cex.lab=1.5,cex.axis=2.0)
abline(1,1,lwd=3.0)

Tree3<-PonderosaTrunc$Tree3[1:9264]
plot(RepeatedFit,Tree3,col=adjustcolor("black",alpha.f = .05),pch=19,xlab="Hourly Phloem Measurement",ylab="Modeled Hourly Temperature",
     main="Ponderosa Pine 3",cex=1.2,cex.main=2.0,cex.lab=1.5,cex.axis=2.0)
abline(1,1,lwd=3.0)

Tree4<-PonderosaTrunc$Tree4[1:9264]
plot(RepeatedFit,Tree4,col=adjustcolor("black",alpha.f = .05),pch=19,xlab="Hourly Phloem Measurement",ylab="Modeled Hourly Temperature",
     main="Ponderosa Pine 4",cex=1.2,cex.main=2.0,cex.lab=1.5,cex.axis=2.0)
abline(1,1,lwd=3.0)
dev.off()
```


